---
title: "R Conference Events Explorer"
author: "Aman Bhatt"
output:
  flexdashboard::flex_dashboard:
    theme: paper
    source_code: embed
---

```{r setup, include=FALSE}
# prep workspace

library(dplyr)  # tidy data manipulation
library(leaflet)  # interative mapping
library(tidyverse)
library(crosstalk)  # inter-widget interactivity
library(DT)
mydata <- readRDS(".\\R_Events.rds")
sch<<-NULL
for(element in mydata){
  sch<-rbind(sch,element)
}

sch <- filter(sch, is.na(venue_lat) == FALSE, is.na(venue_lon)== FALSE)
sch <- sch[,-c(19,20,21)]
sd <- SharedData$new(sch)

```

Interactives {data-icon="ion-stats-bars"}
=====================================  

Column {data-width=400}
-------------------------------------

### Filters

```{r filters}
filter_select(
  id = "venue_city",
  label = "City",
  sharedData = sd,
  group = ~venue_city
)
bscols(

  filter_checkbox(
    id = "status",
    label = "Status",
    sharedData = sd,
    group = ~status
  )
)
bscols(
  filter_slider(
    id = "yes_rsvp_count",
    label = "Rsvp count",
    sharedData = sd,
    column = ~yes_rsvp_count,
    step = 1,
    round = TRUE,
    sep = "",
    ticks = FALSE
  )
)


```


### Datatable {data-height=600}
    
```{r datatable}
sd %>% 
  DT::datatable(
    filter = "top",  # allows filtering on each column
    extensions = c(
      "Buttons",  # add download buttons, etc
       "Scroller" # for scrolling down the rows rather than pagination
    ),
    rownames = FALSE,  # remove rownames
    style = "bootstrap",
    class = "compact",
    width = "100%",
    options = list(
      dom = "Blrtip",  # specify content (search box, etc)
      deferRender = TRUE,
       scrollY = 200,
      scroller = TRUE,
      columnDefs = list(
        list(
          visible = FALSE,
          targets = c(2, 3, 5:15)
        )
      ), 
      buttons = list(
        I("colvis"),  # turn columns on and off
        "csv",  # download as .csv
        "excel"  # download as .xlsx
      )
    ),
    colnames = c(
      "Name" = "venue_name",
      "Id" = "id",
      "Status" = "status",
      "date" = "local_date",
      "time" = "local_time",
      "latitude" = "venue_lat",
      "longitude" = "venue_lon",
      "address" = "venue_address_1",
      "city" = "venue_city",
      "country" = "venue_country"
    )
  )
```






Column {data-width=600}
-------------------------------------
    
### Interactive map
    
```{r map}


#main work --------------------------------


 sd %>% 
  leaflet::leaflet() %>%
  leaflet::addProviderTiles(providers$OpenStreetMap,options = providerTileOptions(minZoom = 2, maxZoom = 100)) %>% 
  leaflet::addAwesomeMarkers(
    lng = sch$venue_lon,
    lat = sch$venue_lat,
    popup = ~paste0(
      "<h1>", sch$name, "</h1>",
      
      "<table style='width:100%'>",
      
      "<tr>",
      "<th>Venue Name</th>",
      "<th>", sch$venue_name, "</th>",
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Date</th>",
      "<th>", sch$local_date, "</th>",
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Time</th>",
      "<th>", sch$time, "</th>",
      "</tr>",
      
       "<tr>",
      "<tr>",
      "<th>City</th>",
      "<th>", sch$venue_city, "</th>",
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Location</th>",
      "<th>", sch$venue_address_1, ", ", sch$venue_zip, "</th>",
      "</tr>",
      
      "<tr>",
      "<tr>",
      "<th>Country</th>",
      "<th>", sch$venue_country, "</th>",
      "</tr>"
    ), #end popup()
    datatable(sd, extensions="Scroller", style="bootstrap", class="compact", width="100%",
    options=list(deferRender=TRUE, scrollY=300, scroller=TRUE))
)


```

Information {data-orientation=rows data-icon="fa-info-circle"}
===================================== 



Column {data-width=400}
-------------------------------------

### About

#### How to

* click to grab and drag the map around
* zoom with the '+' and '--' buttons (top-left) or with your mouse's scroll wheel
* click a marker to reveal a popup with information about that school


> Made by Aman Bhatt
>
>GSOC Project
>




